---
title: "Getting started with R"
author: Bochra chemam
date: today
format: html
---

### Exercise 1 {#sec-1}

* Create a vector of the letters A, B and C.

```{r}
# Your answer in code
 c("A","B","C")
```
> Your answer as text



* Assign the vector to a variable `my_letters`
```{r}
# Your answer in code
my_letters <- c("A","B","C")
```


* Check the what happens when you run `letters` (just this) on the command line.
```{r}
# Your answer in code
[1] "a" "b" "c" "d" "e" "f" "g" "h" "i" "j" "k" "l" "m" "n" "o" "p" "q" "r" "s" "t" "u" "v" "w"
[24] "x" "y" "z"
```

> Your answer as text



* What happens when you concatenate two vectors? Add `c(my_letters , my_letters)`
```{r}
# Your answer in code
[1] "A" "B" "C" "A" "B" "C"

```

> Your answer as text



* Add the number 1 to letters. What happens to the type of the vector?
```{r}
# Your answer in code

Error in letters + 1 : non-numeric argument to binary operator
```

> Your answer as text



### Exercise 2


1. Create a vector `my_vec` with the numbers from 1 through 8.
2. Apply the operation `+2` to the vector/
3. Add the vector containing 1, 2, 3, 4 to `my_vec`. What do you observe?

```{r}
# Your answer in code
my_vec <- seq(from = 1, to = 8)
my_vec <- my_vec+2
my_vec <- my_vec+ c(1,2,3,4)


```



### Exercise 3

* Consider the R output of the matrix below:

```
 [,1] [,2]
 [1,]    4    1
 [2,]    9    5
 [3,]   10    7
```

1. What was one of the correct commands used to write this matrix?
2. Assign the matrix as `A`
3. Check the dimensions
4. Extract the element `5`
5. Add the vector `c(0,0,0)` as a new column and update `A`
6. Modify the element 4 to `0`
7. Compute the transpose of `A`

```{r}
# Your answer in code
matrix(1:6, nrow = 3)
A <- matrix(1:6, nrow = 3)
dim(A)




```


8. Are any values in `A` larger than 10? 
```{r}
# Your answer in code

```

9. Are all values in `A` smaller than 10?
```{r}
# Your answer in code

```

### Exercise 4

1. Create a function that sums up two values even if provided as characters values

```{r}
# Your answer in code





```


### Exercise 5

1. Create a function that returns the mean, median and standard deviation.

```{r}
# Your answer in code



```


### Exercise 6
1. Create a pipe statement that counts the number of NAs in vector containing numbers, characters and missing values.
The output of `c('1' , "a", NA, "2", NA)` should be 2.

```{r}
# Your answer in code



```


